---
title: "lab17"
author: "sieun Bae"
date: '2019 5 14 '
output: html_document
---
0) Ensure the ’dplyr’, ‘magrittr’ and ‘gapminder’ packages are installed and loaded. We’ll be working with the gapminder dataset.
```{r}
library(dplyr)
library(magrittr)
library(gapminder)
```

1) Create a vector c(1, 2, 3, 3, 2, 1) and run min_rank(), dense_rank() and row_number() on it. What are the output for each?
```{r}
vec <- c(1,2,3,3,2,1)
min_rank(vec)
dense_rank(vec)
row_number(vec)
```

Answer: 1 3 5 5 3 1 
Answer: 1 2 3 3 2 1 
Answer: 1 3 4 5 4 2

2) Create a copy of gapminder by assigning it to my_gap
```{r}
my_gap <- data.frame(gapminder)
```

3) Use piping to select all rows for the country “Korea, Rep.” How many rows were returned?
Code
```{r}
my_gap %>% filter(country == "Korea, Rep.") %>% nrow
```
Answer: 12

4) How many observations do we have per continent?
Code
```{r}
my_gap %>% count(continent)
table(my_gap$continent)
```
Answer: Africa - 624, Americas - 300, Asia - 396, Europe - 360, Oceania - 24

5) Find the countries with the lowest and highest life expectancies. Use
min_rank()
Code
```{r}
my_gap %>% select(country, lifeExp) %>% filter(min_rank(lifeExp) == 1 | min_rank(desc(lifeExp)) == 1) %>% arrange(lifeExp)
```
Answer: (lowest) Rwanda - 23.599, (highest) Japan - 82.603

6) Find the countries with the lowest and highest life expectancies over time (grouped by year). Use min_rank(). Which countries had the lowest and highest life expectancies in 1977?
Code
```{r}
my_gap %>% select(country, lifeExp, year) %>% group_by(year) %>% filter(min_rank(lifeExp) == 1 | min_rank(desc(lifeExp)) == 1) %>% arrange(year)
```

Answer: (lowest) Cambodia - 31.220, (highest) Iceland - 76.110

7) How many countries are there in each continent? You may want to summarise and and use n_distinct()
Code
```{r}
my_gap %>% group_by(continent) %>% summarise(numberOfCountry = n_distinct(country))
```
Answer: Africa - 52, Americas - 25, Asia - 33, Europe - 30, Oceania - 2

8) Working only with countries in Africa, get the countries with the lowest life expectancies over time (grouped by year). Which country had the lowest
life expectancy in 1987?
Code
```{r}
my_gap %>% filter(continent == "Africa") %>% group_by(year) %>% filter(min_rank(lifeExp) == 1) %>% select(country, lifeExp, year) %>% arrange(year)
```
Answer: Angola

9) Again working only with countries in Africa, get the countries with the highest and lowest life expectancies over time. Use min_rank() again
Code
```{r}
my_gap %>% filter(continent == "Africa") %>% group_by(year) %>% filter(min_rank(lifeExp) == 1 | min_rank(desc(lifeExp)) == 1) %>% select(country, lifeExp, year) %>% arrange(year)
```
 
10) Working with Africa, create a new row with the ranking of the life expectancy (lifeRank), 1 for the lowest life expectancy within Africa and filter only "Gambia", "Sierra Leone", "Reunion", “Rwanda" after the year 2000. You may need to create a separate data for the african continent only for this to get accurate ranking. How many times is Sierra Leone ranked 1?
```{r}
my_gap %>% filter(continent == "Africa") %>% group_by(year) %>% filter(min_rank(lifeExp) == 1) %>% select(country, lifeExp, year) -> temp

temp %>%  filter(year > 2000 & (country == "Gambia" | country == "Sierra Leone" | country == "Reunion" | country == "Rwanda")) -> afterTemp

left_join(temp, afterTemp) %>% arrange(year) %>% filter(country == "Sierra Leone") %>% nrow
```

Answer: 6 times

11) Which country experienced the worst 5-year drop in life expectancy in each continent? You may want to create a new row containing the difference between the current and previous life expectancy given by lag() and then summarising on this value to get the smallest difference for each country and only taking the country with the smallest difference per continent.
Code
```{r}
my_gap %>% arrange(continent, country, year) %>% mutate(countryLag = lag(country,1), lifeExpLag = lag(lifeExp,1)) %>% filter(country == countryLag) %>% group_by(continent) %>% summarise(min_drop = min(lifeExp-lifeExpLag))
```

Joins
12) Inspect the country_codes dataset. We want to join this data with the gapminder data. Only taking the country and continent columns, perform a left_join between gapminder and country_codes. Return only one row per country, i.e. there should not be duplicate rows. (Hint: Try using distinct() or slice())
Code
```{r}
data(country_codes)
data(gapminder)

gapminder %>% select(country, continent) %>% left_join(country_codes) %>% distinct
```
13) Try other join functions such as inner_join() and full_join() to see what the differences are. You may also want to try to join with country_colors
Code
```{r}
gapminder %>% select(country, continent) %>% inner_join(country_codes) %>% distinct #142
gapminder %>% select(country, continent) %>% full_join(country_codes) %>% distinct #187
```
