---
title: "lab16_dplyr"
author: "sieun Bae"
date: '2019 5 9 '
exe_src: 'Gaya Nadarajan Data Science and R (SKKU)'
output: html_document
---

0) Ensure the ’dplyr’ and ‘ggplot2’ packages are installed and loaded. We’ll be working with the diamonds dataset loaded in ggplot2.
```{r}
library(dplyr)
library(ggplot2)
data(diamonds)
```

1)dplyr verbs: Use dplyr verbs to answer question 1
a) Find all diamonds with clarity "I1"
Code
```{r}
filter(diamonds, clarity=="I1")
```

b) Find all diamonds priced between $8000 and $10000
Code
```{r}
filter(diamonds, price>=8000 & price<10000)
```

c) How many diamonds have weight more than 4 carat? Display their weight, cut, color and clarity
Code
```{r}
select(filter(diamonds, carat > 4), carat, cut, color, clarity)
nrow(select(filter(diamonds, carat > 4), carat, cut, color, clarity))
```
Answer
: 5

d) Find all diamonds that have the best color or the best clarity. Display their weight, cut, color and clarity
Code
```{r}
select(filter(diamonds, color == 'D' | clarity == 'IF'), carat, cut, color, clarity)
```

e) Order the diamonds according to their weight, carat. 
What are the cuts of the 3 heaviest diamonds?
Code
```{r}
head(arrange(diamonds, desc(carat)), 3)
```

f) Create a new column price.per.weight which is the price of the diamond per carat
Code
```{r}
mutate(diamonds, price.per.weight = price / carat)
diamonds <- mutate(diamonds, price.per.weight = price / carat)
```

g) Arrange diamonds by the highest price per weight and View the result.
Code
```{r}
View(arrange(diamonds, desc(price.per.weight)))
```

h) Try to think of ways to summarise (group) the color of diamonds based on its price. Provide 3-5 summarise functions
Code
```{r}
by_Color <- group_by(diamonds, color)
summarise(by_Color, max(price), mean(price), min(price))
```

2) Piping (%>%)
Ensure the ‘magrittr’ package is installed and loaded
Use the piping operator to answer the following questions. Repeat questions 1a) - g) using the piping operator.
```{r}
library(magrittr)
```

a) Find all diamonds with clarity "I1”
Code
```{r}
diamonds %>% filter(clarity=="I1")
```

b) Find all diamonds priced between $8000 and $10000
Code
```{r}
diamonds %>% filter(price>=8000 & price<10000)
```

c) How many diamonds have weight more than 4 carat? Display their weight, cut, color and clarity
Code
```{r}
diamonds %>% filter(carat > 4) %>% select(carat, cut, color, clarity) %>% nrow
```
Answer
: 5

d) Find all diamonds that have the best color or the best clarity. Display their weight, cut, color and clarity
Code
```{r}
diamonds %>% filter(color == 'D' | clarity == 'IF') %>% select(carat, cut, color, clarity)
```

e) Order the diamonds according to their weight, carat. What are the cuts of
the 3 heaviest diamonds?
Code
```{r}
diamonds %>% arrange(desc(carat)) %>% head(3)
```

f) Create a new column price.per.weight which is the price of the dia- mond per carat
Code
```{r}
diamonds %>% mutate(price.per.weight = price / carat)
```

g) Arrange diamonds by the highest price per weight and View the result. 
Code
```{r}
diamonds %>% arrange(desc(price.per.weight)) %>% View
```

h) Summarise (group) the cut of diamonds based on its weight. Provide 3-5 summarise functions (one being n()), and then exclude those with counts less than 2000 and order by cut in descending order
Code
```{r}
diamonds %>% group_by(cut) %>% 
  summarise(max = max(carat), 
            mean = mean(carat), 
            min = min(carat),
            quantity = n()) %>%
  filter(quantity>2000) %>%
  arrange(desc(cut))
```
