---
title: "Lab15"
author: "sieun Bae"
date: '2019 5 7 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

function, apply, lapply, sapply
1) Write a function toCelcius() that converts a temperature given in Fahrenheit (°F) to Celsius (°C). 
The formula of conversion is: °C = (°F − 32) × 5/9

```{r}
toCelcius <- function(Fahrenheit){
  Celcius <- (Fahrenheit-32)*5/9
  
  return(Celcius)
}
```

Determine what input(s) it should take and any output(s) that it should return. 
Call this function with the values given below. What are the equivalent temperatures in Celsius?
50°F, 77°F, 86°F, 98.6°F, 32°F, -40°F

```{r}
toCelcius(50)
toCelcius(77)
toCelcius(86)
toCelcius(98.6)
toCelcius(32)
toCelcius(-40)
```

2) Try to now convert Celsius to Fahrenheit by writing toFahrenheit() function and rearranging the formula above.
```{r}
toFahrenheit <- function(Celsius){
  Fahrenheit <- Celsius*9/5 + 32
  
  return(Fahrenheit)
}

toFahrenheit(10)
toFahrenheit(25)
toFahrenheit(30)
toFahrenheit(37)
toFahrenheit(0)
toFahrenheit(-40)
```

3) Write a function computeMeanCelcius() that computes the mean temperature of its input which is a vector of temperatures in Fahrenheit.
```{r}
computeMeanCelcius <- function(Fahrenheit){
    Celcius <- sapply(Fahrenheit, toCelcius)
    return(mean(Celcius))
}

Fahrenheit <- c(50, 77, 86, 98.6, 32, -40)
computeMeanCelcius(Fahrenheit)
```

4) Write a function that returns TRUE if a number is divisible by 13, FALSE if not.
```{r}
isDiv <- function(num) {
  if (num %% 13 == 0) {
      return (TRUE)
  } else {
      return (FALSE)
  }
}

isDiv(13)
isDiv(16)
```


5) Save the numbers 1 to 1,000,000 into an object named object. 
Apply the previous function in 4) to all the numbers in object. 
Try using a for loop, but also a mapping/apply function.
```{r}
object <- c(1:1000000)
result <- c()

#Using a for loop
usingLoop <- function(object) {
  for (i in 1:length(object)) {
    result[i] <- isDiv(object[i])
  }
  return(result)
}
#Using a apply function
sapply(object, isDiv)
```


6) Write a function someFn() that takes in a single vector argument xvec and returns a vector of the values of the function f(x) given below

f(x)= x2+2x+3 (if x<0)
      x + 3   (if 0<=x<2)
      x2+4x-7 (if x>=2)
      
```{r}

calculate <- function(x){
  if(x<0){
    return (x*x+2*x+3)
  } else if (x>=0 & x<2){
    return (x+3)
  } else{
    return (x*x+4*x-7)
  }
}
someFn <- function(xvec) {
  result <- sapply(xvec, calculate)
  return (result)
}

xvec <- c(-8, 3, 1)
someFn(xvec)
```

      
      
      
      
      
      
      
      
      
      
      
      
      
      
      
      
      
      
      