---
title: "lab10.Rmd"
output: html_document
---

1. Histograms

a) Plot a histogram of the geyser$waiting values using hist(). Do not change any labels yet.
```{r}
library(MASS)
hist(geyser$waiting)
```
b) Tweak the x, y and title labels by adding xlab, ylab and main parameters to the hist() function. Choose also a suitable colour for your histogram.
```{r}
hist(geyser$waiting, main="Waiting time for this eruption", xlab="time", ylab= "frequency", col="purple")
```

c) Observe the break of values in the x-axis. What is the bin width of the histogram (size of each chunk in x axis)?

5

d) Change the break values to break=40:110 in hist() and replot the his- togram. What is the width of the bin now? How would you change the bin width to 2?

```{r}
hist(geyser$waiting, main="Waiting time for this eruption", xlab="time", ylab= "frequency", col="purple", breaks=seq(40,110, by=2))
```

e) Keeping the bin width to 2, change the values in the x-axis by setting the xaxt parameter in hist() to xaxt='n'. Now add a line after plot as follows:
axis(1, at=seq(40,110,by=4), cex.axis=0.5)


```{r}
hist(geyser$waiting, main="Waiting time for this eruption", xlab="time", ylab= "frequency", col="purple", breaks=seq(40,110, by=2), xaxt='n', yaxt='n')
axis(2, at=seq(40,110,by=4), cex.axis=0.5)
```


Figure out what this line is doing by observing the plot. Try to change the values in the y axis with yaxt='n' and axis(2, ...) with suitable parameters

- an integer specifying which side of the plot the axis is to be drawn on
출처: https://rfriend.tistory.com/153 [R, Python 분석과 프로그래밍 (by R Friend)]
- setting the side, but don't draw


2. Scatter Plots

a) Using the dataset painters, plot Colour against the Drawing. The color of the dots are darkmagenta and the pch value is 16.

```{r}
library(MASS)
plot(painters$Colour, painters$Drawing, main="Painters' Colours versus Drawing", type = "p", pch=16, col="darkmagenta")
```


b) Change the x, y and title labels to the ones given above, the color of the
title is deeppink

```{r}
plot(painters$Colour, painters$Drawing, xlab = "Number of colours Used", ylab = "Drawings Done", main="Painters' Colours versus Drawing", type = "p", pch=16, col="darkmagenta", col.main = "deeppink")
```

c) Add a gold vertical line which represents the mean of Colours and a
cornflowerblue horizontal line representing the median of Drawings
```{r}
plot(painters$Colour, painters$Drawing, xlab = "Number of colours Used", ylab = "Drawings Done", main="Painters' Colours versus Drawing", type = "p", pch=16, col="darkmagenta", col.main = "deeppink")
abline(h=median(painters$Drawing), col="cornflowerblue", lty="longdash")
abline(v=mean(painters$Colour), col="gold")
```

d) Change the values in the x and y axes by setting xaxt and yaxt to 'n' in plot and then adding two axis functions (1 for x-axis and 2 for y-axis). Set their cex.axis to 0.6. Finally rotate the values in the y axis by setting las=1

```{r}
plot(painters$Colour, painters$Drawing, xlab = "Number of colours Used", ylab = "Drawings Done", main="Painters' Colours versus Drawing", type = "p", pch=16, col="darkmagenta", col.main = "deeppink", xaxt='n', yaxt='n')
abline(h=median(painters$Drawing), col="cornflowerblue", lty="longdash")
abline(v=mean(painters$Colour), col="gold")
axis(1, at=seq(0,18,by=2), cex.axis = 0.6)
axis(2, at=seq(6,18,by=1),las=1)
```

3. Line plot

Dataset: DDT Parameters: Title color is darkgreen, lwd (line width) set to 2, pch=15, cex=0.7 col is a vector of 2 colours (coral and limegreen).
```{r}
plot(DDT, xlab = "Frequency", ylab = "DDT", main="DDT in Kale", type = "b", pch=15, lwd = 2, col=c("coral", "limegreen"), col.main = 81, xaxt='n', yaxt='n')
axis(1, at=seq(2,14,,by=2), cex.axis = 0.7)
axis(2, at=seq(3.0,4.5,by=0.5),las=1)
```
