---
title: "Lab14"
author: "sieun Bae"
date: '2019 4 25 '
output: html_document
---

0) Ensure the ’ggplot2’ package is installed and loaded.
1) LifeCycleSavings preloaded in R datasets
```{r}
df <- data.frame(LifeCycleSavings)
```

a) Which country has the highest savings rate (sr)?
```{r}
df <- df[order(df$sr, decreasing=TRUE),]
View(df)
rownames(df[1,])
```

b) In these data, if a country has more than 40% of its population under 15 years old, then it has less than 3% of its population over 75 years old.

```{r}

```


c) Investigate potential relationships between variables. Use pairs() with the parameter LifeCycleSavings to see if variables are connected. Which two variables seem to have a positive correlation?
```{r}

```

d) Plot a scatter plot of the variables income dpi and % of population over 75, pop75. Add a third variable savings rate, sr shown as different sizes of the points. In order to give better scaling of the point sizes, add a layer scale_radius(range=c(1, 4)) where range specifies the minimum and maximum sizes of the points. Test with different ranges to see the effects. Do you see any apparent relationship between sr and dpi or pop75?
```{r}

```

e) This time use % of population under 15, pop15 as the variable cut the plot by size of the points, again, use scale_radius() with a suitable range. Is there any connection between percentage of population under 15 and per- centage of population over 75 or income?
```{r}

```

2) ChickWeight preloaded in R datasets
a) Inspect the ChickWeight data by using head() and str(). Draw a line plot geom_line() by mapping Time to x and weight to y for each Chick. To do this add the aesthetic group=Chick into aes()

data(ChickWeight)

```{r}
ggplot(data=ChickWeight, aes(x=Time, y=weight)) +
  geom_line(aes(group=Chick))
```


b) It’s hard to conclude anything from those chaotic lines. Split the data by color using Diet.

```{r}
ggplot(data=ChickWeight, aes(x=Time, y=weight, color = Diet)) +
  geom_line(aes(group=Chick))
```

c) Now we can see the time and weight of each chick with different diets. We are going to add a line for each diet using geom_smooth() with method=lm to represent the best linear model. We want this line to stand out more by set- ting the line width lwd=2 and removing the confidence interval within ge- om_smooth(). Finally we want the other lines to be less transparent by set- ting the alpha in geom_point() to be something suitable, e.g. 0.3

```{r}
ggplot(data=ChickWeight, aes(x=Time, y=weight, color = Diet)) +
  geom_line(aes(group=Chick), alpha=0.3) +
  geom_smooth(method=lm, lwd=2, se=FALSE)
```

3) HairEyeColor preloaded in R datasets
a) Sometimes drawing multiple plots for different values of a categorical (factor) variable is easier to interpret. Firstly, we need to convert the HairEyeColor data which is a table to a data frame. Use as.data.frame() on HairEyeColor and store the resulting data frame in haireyecol

```{r}
haireyecol <- as.data.frame(HairEyeColor)
View(haireyecol)
```

b) Inspect the haireyecol. Why does it have 32 rows?

"Hair"" and "Eye"" has 4 factors each, and there is also the "sex" label, so 4 * 4 * 2 = 32

c) We are going to plot a bar chart using the Eye color and Freq. We can do this by using geom_bar() with aesthetic weight=Freq or drawing a geom_col() with x and y aesthetics Eye and Freq respectively. We also want to stack the different Sex groups in the bar using the fill aesthetic

```{r}
ggplot(haireyecol, aes(x=Eye, y=Freq, fill = Sex)) +
  geom_col()
```

d) Finally we want to see multiple distributions of eye frequencies stacked by gender based on their hair colour. We will use something called facet_wrap() to do this. Add a layer using facet_wrap(~Hair) to your plot to produce the graph shown below

```{r}
ggplot(haireyecol, aes(x=Eye, y=Freq, fill = Sex)) +
  geom_col() +
  facet_wrap(~Hair)
```

e) What is the hair colour of most of the subjects of this dataset? Could you verify this using another graph?
: Brown

```{r}
ggplot(haireyecol, aes(x=Hair, y=Freq)) +
  geom_col()
```

f) What hair color is the least? Again could you verify this graphically?
: Red

g) What is the most common eye color among blond female subjects? What about blond males?
: Blue is the most common eye color among blond female subjects.
: Also Blue is the most common eye color among blond males.

```{r}
ggplot(haireyecol, aes(x=Eye, y=Freq, fill = Sex)) +
  geom_col() +
  facet_wrap(~Hair)
```
































