---
title: "lab18"
author: "sieun Bae"
date: '2019 5 16 '
output: html_document
---
A) T-test
Ensure the ¡¯dplyr¡¯ and ¡®gapminder¡¯ packages are installed and loaded.
We¡¯ll be working with the gapminder dataset.
```{r}
library(dplyr)
library(gapminder)
data("gapminder")
```

1) Get the mean GDP per capita of Canada and Mali. You may want to use
filter(), group_by() and summarise() for this. What is the difference in their GDP per Capita?
Code
```{r}
gapminder %>% filter(country == 'Canada' | country == 'Mali') %>% group_by(country) %>% summarise(mean = mean(gdpPercap))
```
Answer: Canada - 22410.7463,  Mali - 673.0931

2) Perform a t-test to determine if the difference in these GDP per capita are statistically significant or just down to chance. What is the null hypothesis?
You may want to create a data frame that stores the GDP of both these countries and then feed this data into t.test()
Code
```{r}
gapminder %>% filter(country == 'Canada' | country == 'Mali') %>% group_by(country) %>% select(country, gdpPercap) -> df

t.test(data = df, gdpPercap ~ country)
```

Null hypothesis

Is difference real? 
p-value < 0.05 so H rejected and the difference is in fact real

What is the 95% CI if there is a difference?
(16520.52, 26954.78)

3) Pick two countries of your choice and compare if there is a difference in their populations



B) Combining pipes with ggplot2 (Load ggplot2)

https://uomresearchit.github.io/r-tidyverse-intro/aio/

3) Using ggplot and piping, produce a scatter plot of gdpPercap on the xaxis lifeExp on the y-axis for GDPs less than 50,000.
Code
```{r}
library(ggplot2)

gapminder %>% filter(gdpPercap < 50000) %>% ggplot(aes(x=gdpPercap, y=lifeExp)) +
  geom_point()
```

4) Modify the plot above to represent the continents in different colours. Make
the points more transparent by setting the alpha to 0.3. Resize the dots to be
proportional to the size of the population.
Code
```{r}
gapminder %>% filter(gdpPercap < 50000) %>% ggplot(aes(x=gdpPercap, y=lifeExp, size=pop, color = continent)) +
  geom_point(alpha = 0.3)
```

5) Modify the plot above with a log transformation of gdpPercap so the plot
looks more linear and add a line with linear model method
Code
```{r}
gapminder %>% filter(gdpPercap < 50000) %>% ggplot(aes(x=gdpPercap, y=lifeExp, size=pop, color = continent)) +
  geom_point(alpha = 0.3) +
  scale_x_log10()
```

6) Add a facet wrap by continent so the data is neater to view. Replace the
colour split from continent to year.
Code
```{r}
gapminder %>% filter(gdpPercap < 50000) %>% ggplot(aes(x=gdpPercap, y=lifeExp, size=pop, color = year)) +
  geom_point(alpha = 0.3) +
  scale_x_log10() +
  facet_wrap(~ continent)
```

C) Linear Regression ??? gapminder

7) Perform linear regression on the dependent variable gdpPercap against
lifeExp. Save the result in model. View model¡¯s summary. Is the difference between the means of these two variables significant?
Code
```{r}

```
Answer:__________________________________________________


8) Rerun lm() on dependent variable gdpPercap against pop. What is the p
value and is the difference significant?
Code
```{r}

```
Answer:__________________________________________________

9) Create a linear model on gdpPercap against all other variables and view
its summary.
Code
```{r}

```

10) View the attributes of model by typing attributes(model). Access its
residuals and coefficients using $ as with data frames for readability.
Code
```{r}

```
We will work with mtcars dataset. Attach it to R¡¯s search path

11) Study if the miles per gallon (mpg) of a car with less than 5 gears is influenced by its horsepower (hp), weight (wt), displacement (disp) or qsec by
running a linear model on each of them. Which ones are positively correlated
to mpg (coefficient > 0) ?
Code
```{r}

```

Answer:__________________________________________________
