---
title: "Computer price in 90s"
author: "sieun Bae"
date: '2019 4 18 '
output: html_document
---
This is a dataset from the 90s about computer prices. Interesting, let’s dig deeper.
a) Read this file into a data frame called computers using read.csv(). Check the variables in computers using str() or View()

```{r}
df <- read.csv("computer_price.csv")
View(df)
str(df)
```

b) Plot a scatter plot of the speed+hd+ram on the x-axis and the price on the y-axis. Use ggplot() with aes() and geom_points(). Do you see any general pattern between the two variables?

```{r}
ggplot(data=df, aes(x=speed+hd+ram, y=price)) +
  geom_point()
```

c) Transform the x-axis to its log using scale_x_continuous() and add it as a layer to ggplot. Is the pattern clearer now?

```{r}
ggplot(data=df, aes(x=speed+hd+ram, y=price)) +
  geom_point() +
  scale_x_continuous(trans='log')
```

d) Add a regression line using the geom_smooth() function with method=lm. Is price generally higher when speed combined with hard disk and memory is higher?

yes

```{r}
ggplot(data=df, aes(x=speed+hd+ram, y=price)) +
  geom_point() +
  scale_x_continuous(trans='log')+
  geom_smooth(method="lm")
```

e) We now want to study the effect of having a CD drive on top of the speed, hard drive and memory. Split the data by color along the cd variable (add within aes) and remove the geom_smooth() for now. Are computers with a CD drive general more expensive and have higher speed, HD and RAM?

yes

```{r}
ggplot(data=df, mapping = aes(x=speed+hd+ram, y=price,
                              color = as.factor(cd))) +
                              geom_point()
                              scale_x_continuous(trans='log')
```

f) Finally, split the data by color but this time with screen size. What can you conclude about the screen size and the price of the computers?

if size bigger, price goes higher 

```{r}
ggplot(data=df, mapping = aes(x=speed+hd+ram, y=price,
                              color = as.factor(screen))) +
                              geom_point()
                              scale_x_continuous(trans='log')
```
