---
title: "Melanoma"
author: "sieun Bae"
date: '2019 4 18 '
output: html_document
---

```{r}
df <- data.frame(Melanoma)
str(df)
View(df)
```

a) Plot a scatter plot of the age versus thickness variables in the Melanoma dataset. Use ggplot() with aes() to specify the x and y parameters and geom_point()

```{r}
ggplot(data=df, aes(x=age, y=thickness))+
  geom_point()
```

b) Transform the y-axis values to their square root. Use trans=‘sqrt’ in scale_y_continuous() and add it as a layer to your plot

```{r}
ggplot(data=df, aes(x=age, y=thickness)) +
  scale_y_continuous(trans='sqrt')+
  geom_point()
```

c) Change the y axis label to “Tumour Thickness” using the ylab() function added to your plot layer

```{r}
ggplot(data=df, aes(x=age, y=thickness)) +
  scale_y_continuous(trans='sqrt')+
  ylab("Tumour Thickness")+
  geom_point()
```

d) Add a regression line using the geom_smooth() function with method=lm. Within geom_smooth(),set the line’s color to red using col and do not show the confidence interval by setting <<<se=F>>>

```{r}
ggplot(data=df, aes(x=age, y=thickness)) +
  scale_y_continuous(trans='sqrt')+
  ylab("Tumour Thickness")+
  geom_point()+
  geom_smooth(method='lm', col='red', se=FALSE)
```

e) Split the data by colors to denote different sex. Remember to convert sex to a factor first via as.factor(). Is there a pattern between sex and age or sex and tumor thickness?

no

```{r}
ggplot(data=df, aes(x=age, y=thickness,
                    color = as.factor(sex))) +
  scale_y_continuous(trans='sqrt')+
  ylab("Tumour Thickness")+
  geom_point()+
  geom_smooth(method='lm', col='red', se=FALSE)
```

f) Split the data by color again but this time using the ulcer variable. Could also vary the shape of distinct ulcer values by adding shape=as.factor(ulcer) in addition to color in aes(). Is there a relationship between the presence of ulcers with age or tumor thickness?

if ulcers present, higher tumour thickness

```{r}
ggplot(data=df, aes(x=age, y=thickness,
                    color = as.factor(ulcer),
                    shape = as.factor(ulcer))) +
  scale_y_continuous(trans='sqrt')+
  ylab("Tumour Thickness")+
  geom_point()+
  geom_smooth(method='lm', col='red', se=FALSE)
```
